---
title: "Social Survey 2010"
author: "Samantha Lee"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
#names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
First we will compare race with the belief in continental drift.

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```

Looking at the data, there appears to be no significant difference between white and other on the belief of contiental drift, but it appears there is a significant difference between black and white and other with black having more individuals who did not believe in continental drift.




We will now compare race with the agreement of capital punishment.

```{r}
barchartGC(~race+cappun, data=alldata, type = "percent") 
```

There appears to be no significant difference between black and other's opinion on capital punishment, but there is a signifcant difference between white and black and other's opinion on capital punishment with white having more individuals who approve of capital punishment.




We will now compare the belief in continental drift to the opinion of capital punishment.

```{r}
barchartGC(~cappun+condrift, data=alldata, type = "percent") 
```

Looking at the chart, there appears to be no significant difference between those who favor and those who oppose capital punishment and whether or not they believe in continental drift.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
Now we will create a table to view the data for race compared to belief in continental drift.

```{r}
tab1 =xtabs(~race+condrift, data=alldata)
rowPerc(tab1)
colPerc(tab1)
```

Looking at all the data, it appears that black people belive in contintal drift the least with 23.3% not beliving in it, others follow with 9.46% not beliving in it, and white with 8.42%.

We will now create a table to compare race to opinion on capital punishment.

```{r}
tab2 =xtabs(~race+cappun, data=alldata)
rowPerc(tab2)
colPerc(tab2)
```

Looking at the data, it appears individuals who identify as white favor capital punishment the most with 72.74% in favor, other has 56.47% in favor, and black is the least in favor with 46.79% in favor.

We will create a table to compare the belief in continental drift to the opinion of capital punishment.

```{r}
tab3 =xtabs(~cappun+condrift, data=alldata)
rowPerc(tab3)
colPerc(tab3)
```

Looking at the data, it appears that there is only a small difference between those who favor and oppose capital punishment and their belief in continental drift.  Those who favor capital punishment has about 89.58% who believe in continental drift and those who oppose has about 88.67% who belives in continental drift.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$ The belief of continental drift, the stance on capitol punisment, and race are dependent of eachother.  

$H_a$ The belief of continental drift, the stance on capitol punishment, and race are indepedent of eachother.  


We will now preform the Chi Squared test to determine the significance of these results.

```{r}
chisqtestGC(tab1, graph=TRUE)
```
```{r}
chisqtestGC(tab2, graph=TRUE)
```

```{r}
chisqtestGC(tab3, graph=TRUE)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
After looking at our graphs and tables, it appears that race, belief in continental drift, and opinion on the death penealty are independent of eachother.  Afther preforming the Chi-Square test. The results for of the tests were significant except for in the comparison of belief in continental drift and the opinion on the death penalty which has a P-value of .7919. Since the P-value is greater than .05 we fail to reject the null hypothesis.